CODECHECK: An open-science initiative to facilitate sharing of computer programs and results presented in scientific publications.

### 2020-10-01 codecheck-paper.tex
add link to repo and add overall TODO
minor updates in introduction, scale Figure 1 to use less than full page

\begin{document}
\title{CODECHECK: An open-science initiative to facilitate sharing of
  computer programs and results presented in scientific publications.}
\author[1,$\ast$]{Daniel N\"{u}st}
\author[2,$\ast$]{Stephen J Eglen}
\affil[1]{\url{https://orcid.org/0000-0002-0024-5046}}
\affil[2]{\url{https://orcid.org/0000-0001-8607-8025}}
\affil[$\ast$]{Contributed equally}
\maketitle
\begin{abstract}
\ldots{}
\end{abstract}

@@

\begin{itemize}
\item Check with Giuliano re: ``code works''. Write to Naomi.
\item Use "execution" insteand of "sharing" in title?
\item Can we introduce "research compendium" as a term?
\end{itemize}

@@

Many areas of scientific research now use computation to either simulate
or analyse their data. These computations are increasingly complex, and
difficult to explain coherently in a paper \citep{marwick_how_2015}. To complement the
traditional route of sharing research by writing papers, there is a
growing trend/demand to share the underlying artifacts, notably code and
datasets, so that others can inspect, reproduce or expand that work
(Figure 1). Some of the earliest proponents were Buckheit and Donoho \cite{buckheit_wavelab_1995} who coined what has been called 
\emph{Claerbout's claim} (extending on \citet{claerbout_electronic_1992}):
\emph{"An article about computational science in a scientific publication 
is \text{not} the scholarship itself, it is merely \textbf{advertising} of
the scholarship. The actual scholarship is the complete software development
environment and the complete set of instructions which generated the 
figures."}
%  Donoho (2010) has another paraphrasing of the same quote, which might work better:
% "an article about computational result is advertising, not scholarship. The actual scholarship is the full software environment, code and data, that produced the result."

@@

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{figs/rr.pdf}
  \caption{The inverse problem in reproducible research.  The left
  half of the diagram shows the diverse range of materials used
  internally within a laboratory.  These materials are often then
  condensed into a paper for sharing with the outside world via the
  research paper, a static PDF document.  Working backwards from the
  PDF to the underlying materials is impossible. This probihibits reuse
  and is not only non-transparent for a specific paper, but also 
  ineffective for science as a whole. By sharing the
  materials on the left, others outside the lab are able to reproduce
  or build on this work.}
  \label{fig:inverse}
\end{figure}

>>>>

\begin{document}
\title{CODECHECK: An open-science initiative to facilitate sharing of
  computer programs and results presented in scientific publications.}
\author[1,$\ast$]{Daniel N\"{u}st}
\author[2,$\ast$]{Stephen J Eglen}
\affil[1]{\url{https://orcid.org/0000-0002-0024-5046}}
\affil[2]{\url{https://orcid.org/0000-0001-8607-8025}}
\affil[$\ast$]{Contributed equally}
\affil[$$]{Public project for this article is at \url{https://github.com/codecheckers/paper}}
\maketitle
\begin{abstract}
\ldots{}
\end{abstract}

@@

\begin{itemize}
\item Check with Giuliano re: ``code works''. Write to Naomi.
\item Use "execution" insteand of "sharing" in title?
\item Can we introduce "research compendium" as a term?
\item Should we make code and data sharing a prerequisite or leave that door open?
\end{itemize}

@@

Many areas of scientific research now use computation to either simulate
or analyse their data. These computations are increasingly complex, and
difficult to explain coherently in a paper \citep{marwick_how_2015}.
To complement the traditional route of sharing research by writing papers,
there is a growing trend/demand to share the underlying artifacts, notably 
code and datasets, so that others can inspect, reproduce or expand that work
(see Figure~\ref{fig:inverse}).
Some of the earliest proponents were Buckheit and Donoho
\cite{buckheit_wavelab_1995} who coined what has been called 
\emph{Claerbout's claim} (extending on \citet{claerbout_electronic_1992}):
\emph{"An article about computational science in a scientific publication 
is \text{not} the scholarship itself, it is merely \textbf{advertising} of
the scholarship. The actual scholarship is the complete software development
environment and the complete set of instructions which generated the 
figures."}
%  Donoho (2010) has another paraphrasing of the same quote, which might work better:
% "an article about computational result is advertising, not scholarship. The actual scholarship is the full software environment, code and data, that produced the result."

@@

\begin{figure}
  \centering
  \includegraphics[width=0.7\textwidth]{figs/rr.pdf}
  \caption{The inverse problem in reproducible research.  The left
  half of the diagram shows the diverse range of materials used
  internally within a laboratory.  These materials are often then
  condensed into a paper for sharing with the outside world via the
  research paper, a static PDF document.  Working backwards from the
  PDF to the underlying materials is impossible. This probihibits reuse
  and is not only non-transparent for a specific paper, but also 
  ineffective for science as a whole. By sharing the
  materials on the left, others outside the lab are able to reproduce
  or build on this work.}
  \label{fig:inverse}
\end{figure}
